%-------------------------
% Resume in LaTeX
% Adapted from Jake Gutierrez template
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage{XCharter} % Clean, professional serif; sharp on screen and in print
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensures ATS / copy-paste extracts clean text from the PDF.
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ahmed Moussaoui}
\end{center}
\vspace{1pt}
{\small
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  541-908-6657 & \href{https://ahmedmoui.github.io}{\underline{ahmedmoui.github.io}} $|$ \href{https://linkedin.com/in/ahmed-latif-moussaoui}{\underline{linkedin.com/in/ahmed-latif-moussaoui}} \\
  \href{mailto:ahmedamoussaoui@gmail.com}{\underline{ahmedamoussaoui@gmail.com}} & Corvallis, OR (Open to Relocation) \\
\end{tabular*}
}
\vspace{-8pt}

%-----------SUMMARY-----------
\section{Summary}
\vspace{-2pt}
\small{Mechanical engineering graduate from Oregon State University (Robotics Control Option) who designs, fabricates, and tests electro-mechanical hardware end to end. Built robotic manipulator systems, autonomous aircraft, and custom structural enclosures from CAD through assembly and verification. Comfortable on the shop floor and in motion-planning code.}
\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oregon State University}{Corvallis, OR}
      {B.S. in Mechanical Engineering, Robotics Control Option}{June 2026}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{CAD and Design}{: SolidWorks, Fusion 360, Autodesk Inventor, GD\&T, DFM, Part and Assembly Design} \\
     \textbf{Fabrication}{: 3D Printing (FDM), Rapid Prototyping, CNC Machining, Soldering, Wiring and Electrical Assembly, Machine Shop} \\
     \textbf{Robotics}{: ROS2, MoveIt2, ArduPilot, Mission Planner, Motion Planning, Systems Integration, Embedded Systems} \\
     \textbf{Programming}{: Python, C++, MATLAB, Arduino, OpenCV, YOLO, Docker, Linux, GitHub} \\
     \textbf{AI and ML}{: AI API Integration, Computer Vision (OpenCV, YOLO), Pre-trained Model Deployment, Model Fine-tuning} \\
     \textbf{Platforms}{: Linux, Raspberry Pi, Raspberry Pi OS}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Robotics Lab Engineer}{Feb. 2025 -- Present}
      {OSU College of Civil Engineering}{Corvallis, OR}
      \resumeItemListStart
        \resumeItem{Led 2--3 engineers automating repetitive material testing with a 7-DOF robotic manipulator.}
        \resumeItem{Built a vision-guided pick-and-place pipeline from scratch, cutting technician task time 75\%.}
        \resumeItem{Presented working hardware capabilities and progress directly to prospective investors.}
        \resumeItem{Containerized the system with Docker for reproducible deployment across lab setups.}
        % CONFIRM-OR-DELETE: Only keep the next line if you actually produced dimensioned, toleranced drawings.
        % \resumeItem{Produced GD\&T-toleranced fabrication drawings for [PART] used in machining and assembly.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Learning Assistant, ME 203}{Sept. 2025 -- Present}
      {OSU MIME Department}{Corvallis, OR}
      \resumeItemListStart
        \resumeItem{Taught Python data analysis and numerical methods to 25+ engineering students per term.}
        \resumeItem{Ran lab sessions and one-on-one tutoring, refining course materials with faculty.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Autonomous RC Aircraft} $|$ \emph{ArduPilot, Mission Planner, Avionics, Fabrication}}{Sept. 2024 -- June 2025}
          \resumeItemListStart
            \resumeItem{Led the autonomous sub-team on a 6--10 person DBF capstone, building the aircraft from scratch including frame, wiring harness, and avionics integration.}
            \resumeItem{Achieved the first successful autonomous test flights in the team's history, across multiple test days.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{SAMI Humanoid Robot} $|$ \emph{ROS2, Pygame, Fusion 360, Raspberry Pi}}{Spring 2025}
          \resumeItemListStart
            \resumeItem{Designed and fabricated the full robot head enclosure and screen mount in Fusion 360 on a 3--5 person team, and built an animated face display with real-time ROS2 emotion-state control.}
            \resumeItem{Delivered a live audience demo of three modes (pose mirroring, dancing, emotional display) with continuous reliable operation.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated Security Door System} $|$ \emph{C++, Arduino, Fusion 360, 3D Printing}}{OSU ME 351}
          \resumeItemListStart
            \resumeItem{Designed and 3D printed the full mechanical enclosure, integrating servo actuation, linkages, and sensors to halve part count and improve manufacturability.}
            \resumeItem{Built a custom metal-detector circuit from scratch and wrote a 5-state C++ control system with jam detection, forced-entry detection, and manual override.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Head Coach, Esports Club}{Sept. 2024 -- Apr. 2025}
      {Oregon State University}{Corvallis, OR}
      \resumeItemListStart
        \resumeItem{Coached and managed around 20 players across two competitive Valorant teams, improving in-game coordination through structured communication and teamwork drills.}
      \resumeItemListEnd

    \resumeSubheading
      {Vice President, LEGO Club}{Nov. 2024 -- Apr. 2025}
      {Oregon State University}{Corvallis, OR}
      \resumeItemListStart
        \resumeItem{Co-founded the club with faculty support and grew membership to 20+ students in one term through weekly build meetings and hands-on engineering activities.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}